The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-01-31 Text/paper.tex
Finished adding data to rdeep and rand

\section{Experimental setup}
To answer our research question, multiple Schnapsen tournaments were held. Each machine-learning bot played multiple 120 game tournaments against each individual non-learning bot. Each learning bot played 9 tournaments with 3 different models against each static bot.
The non-machine learning opponents were:
 \begin{itemize}
\item Bully
\item Rand
\item Rdeep
\end{itemize}
The research procedure was as follows:
\begin{itemize}
\item Training
\item 120 game tournament
\item 120 game tournament
\item 120 game tournament
\end{itemize}

>>>>

\section{Experimental setup}

WORK IN PROGRESSSS

To answer our research question, multiple Schnapsen tournaments were held. Each learning bot played multiple 120 game tournaments against each individual non-learning bot. Each learning bot played a total of 9 tournaments with 3 different models against each static bot.
\subsection{The bots}
The non- learning opponents were Rand, Bully and Rdeep. The learning components we created were:
\begin{description}
\item [ml\_minimal:] asdf
\item [ml\_stripped:]  asdf
\item [ml:] This ml bot is provided by the framework and consists of the  \textit{default feature space} 
\item [ml\_enriched:]  asdf
\item [ml\_advanced:] asdf
\end{description}

The research procedure was as follows:
\begin{itemize}
\item Training
\item 120 game tournament
\item 120 game tournament
\item 120 game tournament
\end{itemize}
